---
title: "HW 9"
author: ""
date: ""
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rstanarm)
options(mc.cores = parallel::detectCores())
```

For this homework, recall the Garmin dataset from the midterm exam. 

```{r}
Garmin <- read_csv("https://raw.githubusercontent.com/STAT505/2022midterm/main/Garmin_clean.csv") 
```


#### 1. (4 points) 

Use the following model and conduct a posterior predictive check of your model / prior.

```{r}
bayes_1 <- stan_glm(heart_rate ~ speed_past_60_seconds * walk, data = Garmin)
```

Create a series of figures and comment on the differences between your predicted datasets and the data.

#### 2. (4 points) 

Using `AIC()`, and `lm()`, compare the following models:

- `heart_rate ~ speed_past_60_seconds * walk`
- `heart_rate ~ speed_past_60_seconds + walk`
- `heart_rate ~ speed_past_60_seconds`
- `heart_rate ~ walk`

Which model do you prefer and why?

#### 3. (4 points) 

Using `loo()`, and `stan_glm()`, compare the following models:

- `heart_rate ~ speed_past_60_seconds * walk`
- `heart_rate ~ speed_past_60_seconds + walk`
- `heart_rate ~ speed_past_60_seconds`
- `heart_rate ~ walk`

Which model do you prefer and why?

#### 4. (4 points) 

Critique the figure below and create a better way to illustrate how heart rate can be used to predict whether a runner was walking or running.
```{r}
Garmin_binary <- Garmin %>% mutate(walked = as.numeric(walk == "walk"), 
                                   heart_rate_diff150 = heart_rate - 150)

Garmin_binary %>% ggplot(aes(y = walked, x = heart_rate)) +
  geom_smooth(method ='loess', formula = 'y~x', color = 'red') +
  geom_smooth(method ='lm', formula = 'y~x', color = 'purple') + geom_point(alpha = .2)

```

#### 5. (4 points) 

Summarize the model output below - feel free to choose whether you summarize the `glm` or `stan_glm` output.
```{r}
Garmin_binary %>% stan_glm(walked ~ heart_rate_diff150, family = 'binomial', data = ., refresh = 0) %>% print(digits = 2)

Garmin_binary %>% glm(walked ~ heart_rate_diff150, family = 'binomial', data = .) %>% summary()

```

